---
title: "Assignment : Task III"
author: "Junhao Zhang"
date: "13/12/2020"
output: html_document
---

Thid document contains the work for the Task III

Thsi set of data caotains devise five questions on a five point Likert scale that ask members of your group about their experience with your chosen task

Where;
Q1	I consider myself a great jumper
Q2	How often do you exercise?
Q3	Did you feel tired after jumping for 30 seconds?
Q4	Do you have any health condition that makes jumping difficult?
Q5	I consider exercising a joyful activity


And five point Likert scale as follows;

strongly agree/everyday :5	
                        :4	
                        :3	
                        :2	
strongly disagree/rarely:1	


Let's import data 
```{r}
## Data
Data=read.csv("C:/Users/Chathuri/Documents/GitHub/task-I/Task III.csv", header = TRUE)
head(Data)
summary(Data)
data=na.omit(Data)# omit the missing values

```
Lets take the covariance matrix of the data to see the interdependencies
```{r}
#Covariance matrix of the variables
S <- cov(data)
S
```
PCA analysis on the data
```{r}
#Compute the eigenvalues and corresponding eigenvectors of S.

s.eigen <- eigen(S)
s.eigen
``` 
```{r}
#proportion of the total variance explained by the components.

for (s in s.eigen$values) {
  print(s / sum(s.eigen$values))
}

``` 
Lets plot the scree plot to identify the PC

#A scree graph of the eigenvalues 
```{r}
plot(s.eigen$values, xlab = 'Eigenvalue Number', ylab = 'Eigenvalue Size', main = 'Scree Graph')
lines(s.eigen$values)
```
To write the PC
```{r}
s.eigen$vectors
```
PC1 = -0.13 Q1 +0.522 Q2 +0.54 Q3 - 0.24 Q4 - 0.60 Q6
PC1 = -0.13 (I consider myself a great jumper) +0.522 (How often do you exercise?) +0.54 (Did you feel tired after jumping for 30 seconds?) - 0.24 (Do you have any health condition that makes jumping difficult?) - 0.60 (I consider exercising a joyful activity)

Visualize the results
```{r}
#Visualize
library(ggfortify)
library(ggplot2)
pca_res <- prcomp(data, scale. = TRUE)
autoplot(pca_res)
```
