---
title: "Assignment : Task II"
author: "Junhao Zhang"
date: "13/12/2020"
output: html_document
---

Thid document contains the work for the Task II

Let's import data 
There are 6 people who used the Sensor Kinetics Pro app to iOS orAndroid device.
Then they were split into subgroups with each subgroup investigating one measures available in the app. Each subgroup reported back aafter 20min with what they have learned

```{r}
## Data
Data=read.csv("Task II.csv", header = TRUE)
head(Data)
summary(Data)
data=na.omit(Data)# omit the missing values

```
data set contains 6 variables. Name and email address of the member is rocorded. Moreover, number of jumpus and three mesurements were recorded.


Preparing Data
```{r}
# Remove the column with name and email, so it will not be included in the clustering
input=data[,3:6]
input

```

K-means to identify the novices from the experts among the members who used only the app data

Packages required to run KMeans Clustering
```{r}
#factoextra to determine the optimal number clusters for a given clustering methods and for data visualization.
#NbClust for computing about 30 methods at once, in order to find the optimal number of clusters.
# ggplot2 for •	Visualizing
library(factoextra)
library(NbClust)
library(ggplot2)

```
K means Xlustering
```{r}
# run K-means for an arbitrary K=3
kmeans(input,centers=3,nstart=20)
```
However, in k means we have to decide the optimal number of k have better clustering. Therefore, we will see a way to identify the optimal k

We have to standarize the data since variables in the input have different scales

```{r}
# Standardize the data
df <- scale(input)
head(df)
```
We are going to use Elbow method to find the optimum k

```{r}
#plot Elbow to identify the optimum number K
#Elbow Method for finding the optimal number of clusters
set.seed(123)
# Compute and plot wss for k = 2 to k = 6.
k.max <- 6
data <- df
wss <- sapply(1:k.max, 
              function(k){kmeans(data, k, nstart=50,iter.max = 15 )$tot.withinss})
wss
plot(1:k.max, wss,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares")
```
According to the graph it can be identified that optimum k is 3.
let’s choose K = 3 and run the K-means again.
```{r}
set.seed(123)
clusters=kmeans(data,centers=3,nstart=20)
clusters
```
However here we need to identify the novices from the experts
Therefore lets take K=2
```{r}
novices_experts=kmeans(data,centers=2,nstart=20)
novices_experts
```
Here in the output clustering vector shows the two clusters where experts and novices

Now we willVisualize the obtained results 
```{r}
str(novices_experts)
fviz_cluster(novices_experts, data = data.frame(data))
```
Cluster plot gives the two clusters where red colour one indicates the experts and blue colour cluster indicates the novices.

Therefore, following members are identified as experts :dan, Yen-Ling and Qianhui Yuan 
  
And identified novices from the experts are: amanda,daisy ,Aniket ,Junhao Zhang  and Xinyuan. 
